---
title: "Car Wash Market Intelligence & Growth Analytics"
author: "Your Name"
output: html_document
---

## Introduction

This report provides an overview of the car wash market and a sample growth analysis using placeholder data.

## Data Summary

```{r}
source("analysis.R")
print(head(growth_data))
```

## Growth Chart

```{r}
# Plot growth trends using the analysis script
print(
  ggplot(growth_data_long, aes(x = year, y = Sites, color = Company)) +
    geom_line() +
    geom_point() +
    ggtitle("Car Wash Sites Growth (Sample Data)") +
    xlab("Year") +
    ylab("Number of Sites")
)
```

## Conclusion


## Case Studies

### Competitor Growth and Expansion Trends

Major express car wash chains have grown quickly through new builds and acquisitions. Mister Car Wash now operates more than 500 locations nationwide and continues to acquire smaller regional chains. Newer entrants such as ModWash scaled rapidly, adding nearly 100 sites in just a few years, while Quick Quack expanded beyond its California base into several western and southern states. Our analysis shows a highly consolidated market where a handful of super‑chains are capturing market share through aggressive expansion.

### Membership Program ROI Comparison

Unlimited wash memberships typically range from $20–30 per month for a basic exterior package, with premium tiers up to $60. Customers break even after only two or three washes a month because individual washes cost around $10–15. Pricing promotions and multi‑car discounts further improve the ROI for households. For operators, membership programs drive recurring revenue and loyalty; at chains like Mister Car Wash, over 70% of wash volume comes from subscribers.

### Customer Sentiment Insights

Online reviews reveal that speed, value and convenience are the main drivers of positive sentiment. Customers praise quick service, free vacuums and helpful staff. Negative feedback often mentions leftover dirt or brush scratches and occasional billing issues when canceling memberships. Smaller regional brands sometimes outperform national chains on review scores, suggesting that consistent quality and service differentiate the leaders.

### Competitive Threat of Big‑Box Club Car Washes

Warehouse retailers like Costco and Sam’s Club have begun offering members low‑cost express car washes, typically $7–8 per wash. These washes leverage the retailers’ existing traffic and membership base, providing a cheap, convenient alternative to dedicated express chains. While quality may vary, and services are often limited to exterior washes, the pricing can attract price‑sensitive consumers who might otherwise join an unlimited wash club. Traditional car wash chains should monitor this trend and emphasize superior service, technology and convenience to retain customers.

This placeholder report demonstrates the structure for a full market intelligence report.
